Multicast File Transfer Protocol

### 2011-07-13 papers/paper1/paper.tex
yet another revision of Model

\paragraph{Messages.}
File transfer takes place via \emph{messages}.
There are three types of messages in the protocol, the first of which being a \emph{request}.
A \emph{request} contains a file ID and a set of fragment indices.
We implemented requests as the file ID and a set of contiguous regions.  
However, one can envision the request to contain anything that defines a set.
The second message type is a \emph{fragment}, which consists of a file ID, a fragment index, and the data comprising that fragment of the file.
Last is a \emph{match}, which consists of a file ID and a set of matching file IDs.

\paragraph {Tasks.}
MFTP is a peer-to-peer protocol since all participants can act as both a client and a server.
In a simple scenario, if a peer gets a request for a file it has fragments for, it can send those fragments out.
Fragments are periodically broadcast even in the absence of requests to indicate what files exist in the network.
A peer can use requests to poll for fragments of a file which can span from individual fragments to the whole file.
A peer which has successfully downloaded any number of fragments of a file can then serve those fragments.
Matching is a two-step process.
The first step applies a matching function $\mu_0$ to two file IDs to determine whether a match is possible between the two files.  
The second step applies a matching function $\mu_1$ to the two files to determine whether there is a match.
If $\mu_1$($f_1$,$f_2$) is true, $\mu_0$($fid_1$,$fid_2$) must be true.
However, if $\mu_0$($fid_1$,$fid_2$) is true, $\mu_1$($f_1$,$f_2$) does \emph{not} have to be true.

>>>>

\paragraph{Messages.}
File transfer takes place via \emph{messages}.
There are three types of messages in the protocol.
The first message type is a \emph{request}.
A request contains a file ID and a set of fragment indices.
We implemented requests as the file ID and a set of contiguous regions.  
However, one can envision the request to contain anything that defines a set.
The second message type is a \emph{fragment}, which consists of a file ID, a fragment index, and the data comprising that fragment of the file.
Last is a \emph{match}, which consists of a file ID and a set of matching file IDs.

\paragraph {Tasks.}
MFTP is a peer-to-peer protocol because each participant can act as both a client and a server.
A peer can send out any fragments for which it gets a request.
Fragments are periodically broadcast, even in the absence of requests, to indicate what files exist in the network.
A peer can use requests to poll for fragments of a file which can span from individual fragments to the whole file.
A peer which has successfully downloaded any number of fragments of a file can then serve those fragments.

Matching is a two-step process.
The first step applies a matching function $\mu_0$ to two file IDs to determine whether a match is possible between the two files.  
The second step applies a matching function $\mu_1$ to the two files to determine whether there is a match.
If $\mu_1$($f_1$,$f_2$) is true, $\mu_0$($fid_1$,$fid_2$) must be true.
However, if $\mu_0$($fid_1$,$fid_2$) is true, $\mu_1$($f_1$,$f_2$) does \emph{not} have to be true.
